\TheTitle

### 2017-07-15 paper/study.tex
fixing study

\begin{table}[htpb]
  \centering
  \caption{Cross-Commit Results\dmg{Be more descriptive in the captions.People read the papers via tables and
      pictures. What does the table say? e.g. as it can be seen.... tell a story with the picture, instead of asking the
    reader to make up the story... which might be different than the one you want them to have}}
  \label{tab:cross_commit_results}
  \begin{tabular}{ccrl}
    \toprule
    Task & Metric      & $p$-value & Conclusion\\\midrule
    T4   & Correctness & 0.22      & Do not reject $H_0$\\
    T5   & Correctness & 0.04      & Reject $H_0$\\
    T6   & Correctness & 0.13      & Do not reject $H_0$\\
    T7   & Correctness & 0.06      & Do not reject $H_0$\\
    T8   & Correctness & 0.07      & Do not reject $H_0$\\
    T9   & Correctness & 0.04      & Reject $H_0$\\
    T10  & Correctness & 0.62      & Do not reject $H_0$\\

@@

\begin{table*}[htpb]
  \centering
  \caption{Summarized Correctness, Accuracy, and Timing results for the summarization tasks}
  \label{tab:summarization_table}
  \begin{tabular}{ccc}
    % Correctness
    \begin{tabular}{crrc}
      \toprule
      Task                  & $\chi^2$ & $p$-value  & Conclusion\\\midrule
      T4                    & 13.07    & 0.0003     & Reject $H_0$\\
      \multirow{2}{*}{T5}   & 5.14     & 0.0233     & Reject $H_0$\\
                            & 5.14     & 0.0233     & Reject $H_0$\\
      T6                    & 14.06    & 0.0002     & Reject $H_0$\\
      T7                    & 11.07    & 0.0009     & Reject $H_0$\\
      T8                    & 13.07    & 0.0003     & Reject $H_0$\\
      \multirow{2}{*}{T9}   & 4.17     & 0.0412     & Reject $H_0$\\
                            & 6.13     & 0.0133     & Reject $H_0$\\
      T10                   & 4.00     & 0.0455     & Reject $H_0$\\
      \bottomrule
    \end{tabular}
    &

@@

Summaries for correctness, accuracy, and timing are shown in
tables~\ref{tab:summarization_table}.
The full results are as follows;

\dmg{you wrongly use ``semicolon'', you mean ``colon''. Same below...}

@@

\dmg{Emphasize: To summarize...}

\tool is able to assist users with summarizing various aspects of a
merge more quickly and accurately than Gitk. In two tasks, T5 and T9,
correctness was affected by the size of a tree, but in both trees, \tool
was able to provide a statistically significant improvement to the
correctness. Only in one task, T7, was timing affected by the size of a
tree; \tool did not significantly improve the time taken to answer T7 on
the smaller tree, but did improve the time taken on the larger tree.

@@

Among the 12 participants, there was nearly unanimous agreement that for
conceptual understanding and summarization tasks; \dmg{this is another wrong use of semicolon}\tool was easier to
work with \dmg{avoid idiomatic expressions: what does ``work with'' mean? use a precise verb. English is a rich language.} than Gitk. The participants cited the ability to abstract
information about the merge from the clean summarization tables and
simple visualizations \dmg{be precise: from Linvis' clean summarization tables and ... }. Three participants suggested that someone with a
professional understanding of Gitk and the git command-line may be able to
extract a conceptual understanding from the DAG visualization and
perform the summarization tasks. One of these three participants said
that they would prefer to have both tools available, as they are able to
complement each other.

>>>>

\begin{table}[htpb]
  \centering
  \caption{Cross-Commit Metrics: Showing that tree size make a
    difference in the correctness metric for T5 and T9, and the timing
    metric for task T7.}
  \label{tab:cross_commit_results}
  \begin{tabular}{ccrl}
    \toprule
    Task & Metric      & $p$-value & Conclusion\\\midrule
    T4   & Correctness & 0.22      & Do not reject $H_0$\\
    T5   & Correctness & 0.04      & Reject $H_0$\\
    T6   & Correctness & 0.13      & Do not reject $H_0$\\
    T7   & Correctness & 0.06      & Do not reject $H_0$\\
    T8   & Correctness & 0.07      & Do not reject $H_0$\\
    T9   & Correctness & 0.04      & Reject $H_0$\\
    T10  & Correctness & 0.62      & Do not reject $H_0$\\

@@

\begin{table*}[htpb]
  \centering
  \caption{Summarized Correctness, Accuracy, and Timing results for the
    summarization tasks. In all cases except for the timing metric of
    T7, there was a difference between \tool and Gitk.}
  \label{tab:summarization_table}
  \begin{tabular}{ccc}
    % Correctness
    \begin{tabular}{crrc}
      \toprule
      Task                  & $\chi^2$ & $p$-value  & Conclusion\\\midrule
      T4                    & 13.07    & 0.0003     & Reject $H_0$\\
      \multirow{2}{*}{T5}   & 5.14     & 0.0233     & Reject $H_0$\\
                            & 5.14     & 0.0233     & Reject $H_0$\\
      T6                    & 14.06    & 0.0002     & Reject $H_0$\\
      T7                    & 11.07    & 0.0009     & Reject $H_0$\\
      T8                    & 13.07    & 0.0003     & Reject $H_0$\\
      \multirow{2}{*}{T9}   & 4.17     & 0.0412     & Reject $H_0$\\
                            & 6.13     & 0.0133     & Reject $H_0$\\
      T10                   & 4.00     & 0.0455     & Reject $H_0$\\
      \bottomrule
    \end{tabular}
    &

@@

Summaries for correctness, accuracy, and timing are shown in
tables~\ref{tab:summarization_table}.
The full results are as follows:

@@

To summarize, \tool is able to assist users with summarizing various
aspects of a merge more quickly and accurately than Gitk. In two tasks,
T5 and T9, correctness was affected by the size of a tree, but in both
trees, \tool was able to provide a statistically significant improvement
to the correctness. Only in one task, T7, was timing affected by the
size of a tree; \tool did not significantly improve the time taken to
answer T7 on the smaller tree, but did improve the time taken on the
larger tree.

@@

Among the 12 participants, there was nearly unanimous agreement that for
conceptual understanding and summarization tasks, \tool was easier to
use than Gitk. The participants cited the ability to abstract
information about the merge from the clean summarization tables and
simple visualizations as the primary reasons for preferring \tool to
Gitk. Three participants suggested that someone with a professional
understanding of Gitk and the git command-line may be able to extract a
conceptual understanding from the DAG visualization and perform the
summarization tasks. One of these three participants said that they
would prefer to have both tools available, as they are able to
complement each other.
